Static and Dynamic Bethe-Salpeter Equations in the $T$-Matrix Approximation

### 2022-02-15 Manuscript/Tmatrix.tex
clean up tex and figures

\newcommand{\mc}{\multicolumn}
\newcommand{\fnm}{\footnotemark}
\newcommand{\fnt}{\footnotetext}
\newcommand{\tabc}[1]{\multicolumn{1}{c}{#1}}
\newcommand{\SupInf}{\textcolor{blue}{supporting information}}
\newcommand{\QP}{\textsc{quantum package}}
\newcommand{\T}[1]{#1^{\intercal}}

@@

%%% FIGURE 1 %%%
\begin{figure*}[t]
	\includegraphics[width=\textwidth]{H2}
	\caption{Singlet (left) and triplet (right) excitation energies (in \si{\eV}) of \ce{H2} as a function of the internuclear distance $R_{\ce{H-H}}$ (in \si{\angstrom}) computed at the FCI (black), BSE@$G_0W_0$ (blue), and BSE@$G_0T_0$ (red) levels with the cc-pVTZ basis.
	Raw data are reported in {\SupInf}.}
	\label{fig:H2}
\end{figure*}
%%% %%% %%% %%%

%%% FIGURE 2 %%%
\begin{figure}[t]
	\includegraphics[width=\linewidth]{H2_gap}
	\caption{HOMO and LUMO quasiparticle energies as well as HOMO-LUMO gap (in \si{\eV}) of \ce{H2} as a function of the internuclear distance $R_{\ce{H-H}}$ (in \si{\angstrom}) computed at the $G_0W_0$ (blue) and $G_0T_0$ (red) levels with the cc-pVTZ basis.
	Raw data are reported in {\SupInf}.}
	\label{fig:H2_gap}
\end{figure}
%%% %%% %%% %%%

%%% FIGURE 3 %%%
\begin{figure*}[t]
	\includegraphics[width=0.4\linewidth]{H2_dBSE1}
	\hspace{0.1\linewidth}
	\includegraphics[width=0.4\linewidth]{H2_dBSE3}
	\caption{
	Error with respect to FCI for the lowest singlet (left) and the lowest triplet (right) excitation energies of \ce{H2} as a function of the internuclear distance $R_{\ce{H-H}}$ (in \si{\angstrom}) computed within the static schemes (BSE@$G_0W_0$ and BSE@$G_0T_0$) and the dynamically-corrected schemes (dBSE@$G_0W_0$ and dBSE@$G_0T_0$) .
	The cc-pVTZ basis is employed for all calculations.
	Raw data are reported in {\SupInf}.}
	\label{fig:H2_dBSE}
\end{figure*}
%%% %%% %%% %%%

@@

%%% FIGURE 4 %%%
\begin{figure*}[t]
	\includegraphics[width=\textwidth]{BeH2}
	\caption{Singlet (left) and triplet (right) excitation energies (in \si{\eV}) of \ce{BeH2} as a function of the distance $R_{\ce{Be-H}}$ (in \si{\angstrom}) computed at the FCI (black), BSE@$G_0W_0$ (blue), and BSE@$G_0T_0$ (red) levels with the cc-pVDZ basis.
	The dynamically-corrected BSE excitation energies are represented as thin lines for dBSE@$G_0W_0$ (blue) and dBSE@$G_0T_0$ (red).
	Raw data are reported in {\SupInf}.}
	\label{fig:BeH2}
\end{figure*}
%%% %%% %%% %%%

%%% FIGURE 5 %%%
\begin{figure}[t]
	\includegraphics[width=\linewidth]{BeH2_gap}
	\caption{HOMO and LUMO quasiparticle energies as well as HOMO-LUMO gap (in \si{\eV}) of \ce{BeH2} as a function of the internuclear distance $R_{\ce{Be-H}}$ (in \si{\angstrom}) computed at the BSE@$G_0W_0$ (blue) and BSE@$G_0T_0$ (red) levels with the cc-pVDZ basis.
	Raw data are reported in {\SupInf}.}
	\label{fig:BeH2_gap}
\end{figure}
%%% %%% %%% %%%

@@

%%% FIGURE 6 %%%
\begin{figure*}
	\includegraphics[width=\linewidth]{H2O}
	\caption{Error with respect to FCI for the singlet (left) and triplet (right) excitation energies (in \si{\eV}) of \ce{H2O} at equilibrium geometry computed at various levels of theory with the aug-cc-pVDZ basis.
	The geometry and the reference FCI values have been extracted from the QUEST database. \cite{Veril_2021}
	Raw data are reported in {\SupInf}.}
	\label{fig:H2O}
\end{figure*}
%%% %%% %%% %%%

@@

%%% TABLE I %%%
%\begin{table*}
%	\caption{Singlet and triplet excitation energies (in \si{\eV}) of various molecular systems at equilibrium geometry computed at various levels of theory with the aug-cc-pVDZ basis set.
%	The corresponding equilibrium geometries as well as the reference FCI values have been extracted from the QUEST database. \cite{Veril_2021}}
%	\label{tab:mol}
%	\begin{ruledtabular}
%		\begin{tabular}{llccccccccc}
%					&			&		&	\mc{8}{c}{Methods}																\\
%			\cline{4-11}
%			Mol.	&	State	&	Nature						&	CIS		&	CIS(D)	&	TDHF	&	BSE@$G_0W_0$	&	dBSE@$G_0W_0$	&	BSE@$G_0T_0$	&	dBSE@$G_0T_0$	&	FCI	\\
%			\hline
%			\ce{H2O}	&	$^1B_1(n \to 3s)$		&	Ryd.	&	8.66	&	6.61	&	8.61	&	7.70	&	7.62	&	6.84	&	6.80	&	7.53\\
%						&	$^1A_2(n \to 3p)$		&	Ryd.	&	10.34	&	8.33	&	10.30	&	9.41	&	9.34	&	8.60	&	8.56	&	9.32\\
%						&	$^3B_1(n \to 3s)$		&	Ryd.	&	7.98	&	6.69	&	7.86	&	7.23	&	7.09	&	6.30	&	6.23	&	7.14\\
%						&	$^3A_2(n \to 3p)$		&	Ryd.	&	10.01	&	8.70	&	9.89	&	9.22	&	9.11	&	8.36	&	8.29	&	9.14\\
%			\ce{HCl}	&	$^1\Pi$					&	CT		&	8.36	&	7.87	&	8.31	&	8.04	&	7.95	&	7.42	&	7.38	&	7.82\\
%			\ce{HC#CH}	&	$^1\Sigma_u^-(\pps)$	&	Val.	&	6.28	&	6.29	&	5.91	&	7.27	&	6.96	&	5.64	&	5.55	&	7.20\\
%						&	$^1\Delta_u(\pps)$		&	Val.	&	6.62	&	6.97	&	6.44	&	7.61	&	7.33	&	5.87	&	5.81	&	7.51\\
%						&	$^3\Sigma_u^+(\pps)$	&	Val.	&	4.52	&	5.75	&	2.19	&	5.63	&	5.12	&	4.02	&	3.83	&	5.50\\
%						&	$^3\Delta_u(\pps)$		&	Val.	&	5.45	&	6.65	&	4.52	&	6.52	&	6.13	&	4.87	&	4.74	&	6.46\\
%			\ce{H2C=NH}	&	$^1A''(\nps)$			&	Val.	&	5.86	&	4.46	&	5.69	&	6.16	&	5.85	&	4.12	&	4.04	&	5.25\\
%						&	$^3A''(\nps)$			&	Val.	&	4.71	&	4.72	&	4.39	&	5.49	&	4.96	&	3.25	&	3.11	&	4.63\\
%		\end{tabular}
%	\end{ruledtabular}
%\end{table*}
%%% %%% %%% %%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\twocolumngrid
\section*{Data availability statement}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The \hypertarget{SI}{data} that support the findings of this study are openly available in Zenodo at \href{http://doi.org/XX.XXXX/zenodo.XXXXXXX}{http://doi.org/XX.XXXX/zenodo.XXXXXXX}.

>>>>

\newcommand{\mc}{\multicolumn}
\newcommand{\fnm}{\footnotemark}
\newcommand{\fnt}{\footnotetext}
\newcommand{\tabc}[1]{\multicolumn{1}{c}{#1}}
\newcommand{\SupMat}{\textcolor{blue}{supplementary material}}
\newcommand{\QP}{\textsc{quantum package}}
\newcommand{\T}[1]{#1^{\intercal}}

@@

%%% FIGURE 1 %%%
\begin{figure*}[t]
	\includegraphics[width=\textwidth]{fig1}
	\caption{Singlet (left) and triplet (right) excitation energies (in \si{\eV}) of \ce{H2} as a function of the internuclear distance $R_{\ce{H-H}}$ (in \si{\angstrom}) computed at the FCI (black), BSE@$G_0W_0$ (blue), and BSE@$G_0T_0$ (red) levels with the cc-pVTZ basis.
	Raw data are reported in {\SupMat}.}
	\label{fig:H2}
\end{figure*}
%%% %%% %%% %%%

%%% FIGURE 2 %%%
\begin{figure}[t]
	\includegraphics[width=\linewidth]{fig2}
	\caption{HOMO and LUMO quasiparticle energies as well as HOMO-LUMO gap (in \si{\eV}) of \ce{H2} as a function of the internuclear distance $R_{\ce{H-H}}$ (in \si{\angstrom}) computed at the $G_0W_0$ (blue) and $G_0T_0$ (red) levels with the cc-pVTZ basis.
	Raw data are reported in {\SupMat}.}
	\label{fig:H2_gap}
\end{figure}
%%% %%% %%% %%%

%%% FIGURE 3 %%%
\begin{figure*}[t]
	\includegraphics[width=0.4\linewidth]{fig3a}
	\hspace{0.1\linewidth}
	\includegraphics[width=0.4\linewidth]{fig3b}
	\caption{
	Error with respect to FCI for the lowest singlet (left) and the lowest triplet (right) excitation energies of \ce{H2} as a function of the internuclear distance $R_{\ce{H-H}}$ (in \si{\angstrom}) computed within the static schemes (BSE@$G_0W_0$ and BSE@$G_0T_0$) and the dynamically-corrected schemes (dBSE@$G_0W_0$ and dBSE@$G_0T_0$) .
	The cc-pVTZ basis is employed for all calculations.
	Raw data are reported in {\SupMat}.}
	\label{fig:H2_dBSE}
\end{figure*}
%%% %%% %%% %%%

@@

%%% FIGURE 4 %%%
\begin{figure*}[t]
	\includegraphics[width=\textwidth]{fig4}
	\caption{Singlet (left) and triplet (right) excitation energies (in \si{\eV}) of \ce{BeH2} as a function of the distance $R_{\ce{Be-H}}$ (in \si{\angstrom}) computed at the FCI (black), BSE@$G_0W_0$ (blue), and BSE@$G_0T_0$ (red) levels with the cc-pVDZ basis.
	The dynamically-corrected BSE excitation energies are represented as thin lines for dBSE@$G_0W_0$ (blue) and dBSE@$G_0T_0$ (red).
	Raw data are reported in {\SupMat}.}
	\label{fig:BeH2}
\end{figure*}
%%% %%% %%% %%%

%%% FIGURE 5 %%%
\begin{figure}[t]
	\includegraphics[width=\linewidth]{fig5}
	\caption{HOMO and LUMO quasiparticle energies as well as HOMO-LUMO gap (in \si{\eV}) of \ce{BeH2} as a function of the internuclear distance $R_{\ce{Be-H}}$ (in \si{\angstrom}) computed at the BSE@$G_0W_0$ (blue) and BSE@$G_0T_0$ (red) levels with the cc-pVDZ basis.
	Raw data are reported in {\SupMat}.}
	\label{fig:BeH2_gap}
\end{figure}
%%% %%% %%% %%%

@@

%%% FIGURE 6 %%%
\begin{figure*}
	\includegraphics[width=\linewidth]{fig6}
	\caption{Error with respect to FCI for the singlet (left) and triplet (right) excitation energies (in \si{\eV}) of \ce{H2O} at equilibrium geometry computed at various levels of theory with the aug-cc-pVDZ basis.
	The geometry and the reference FCI values have been extracted from the QUEST database. \cite{Veril_2021}
	Raw data are reported in {\SupMat}.}
	\label{fig:H2O}
\end{figure*}
%%% %%% %%% %%%

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\twocolumngrid
\section*{Data availability statement}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The data that supports the findings of this study are available within the article and its supplementary material.
